Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies

### 2021-02-01 manuscript_wesbrook-bigmacc_BS2021.tex

@@

%---------------------------------------------------------------------------------------
\section*{Results}
\begin{figure}[h!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs as described in \ref{fig:true_macc_both}.

@@

% Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario. For each of the four combinations of development and climate change pathway, %Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier. The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%. The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented. These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}.

% is highlighted in Figure \ref{fig:pareto_plot}.

@@

%\begin{figure}[t]
%    \centering
%    \captionsetup{margin=.5cm}
%    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
%    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%    \label{fig:pareto_plot}
%\end{figure}

>>>>

\begin{figure}[t!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

@@

%---------------------------------------------------------------------------------------
\section*{Results}

The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs as described in Figure \ref{fig:true_macc_both}.

@@

\begin{figure}[t!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.45]{figures/pareto_plots_585_box_update.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}, highlighted in Figure \ref{fig:pareto_plot}. Marginal abatement cost and the adaptation metric were plotted in Figure \ref{fig:pareto_plot} to evaluate optimal fronts of each scenario.

@@
